Internal models of type theory

### 2013-10-28 article-models-tt.tex
Started description of the model of equifibered diagrams
introducing judgmental equalities for weakening followed by substitution; introducing identity functions

\begin{align*}
\jctx*{\Gamma} & \jctxeq*{\Gamma}{\Gamma'}\\
\jtermc*{\Gamma}{i} & \jtermc*{\Gamma}{i}{j}\\
\jtype*{\Gamma}{A} & \jtypeeq*{\Gamma}{A}{B}\\
\jtermt*{\Gamma}{A}{x} & \jtermteq*{\Gamma}{A}{x}{y}.
\end{align*}

@@

\subsection{Definitional equality rules for weakening and substitution}

>>>>

\begin{align*}
\jctx*{\Gamma} & \jctxeq*{\Gamma}{\Gamma'}\\
\jtermc*{\Gamma}{i} & \jtermceq*{\Gamma}{i}{j}\\
\jtype*{\Gamma}{A} & \jtypeeq*{\Gamma}{A}{B}\\
\jtermt*{\Gamma}{A}{x} & \jtermteq*{\Gamma}{A}{x}{y}.
\end{align*}

@@

\subsection{Definitional equality rules for weakening and substitution}
The judgmental equalities we're about to describe assert that weakening followed
by substitution leaves everything untouched. Thus, we get that each fiber
$\subst{x}{\ctxwk{A}{B}}$ is just $B$, that $\ctxwk{A}{y}$ is the constant function
mapping everything to $y:B$ and similar properties for families and terms thereof.

\begin{infarray}{c}
\inference{\jtype{\Gamma}{A}\qquad\jtype{\Gamma}{B}\qquad\jtermt{\Gamma}{A}{x}}{\jtypeeq{\Gamma}{\subst{x}{\ctxwk{A}{B}}}{B}}\\
\inference{\jtype{\Gamma}{A}\qquad\jtype{\ctxext{\Gamma}{B}}{Q}\qquad\jtermt{A}{x}}{\jtypeeq{\ctxext{\Gamma}{B}}{\subst{x}{\ctxwk{A}{Q}}}{Q}}\\
\inference{\jtermt{\Gamma}{A}{x}\qquad\jtermt{\Gamma}{B}{y}}{\jtermteq{\Gamma}{B}{\subst{x}{\ctxwk{A}{y}}}{y}}\\
\inference{\jtermt{\Gamma}{A}{x}\qquad\jtermt{\ctxext{\Gamma}{B}}{Q}{g}}{\jtermteq{\ctxext{\Gamma}{B}}{Q}{\subst{x}{\ctxwk{A}{g}}}{g}}
\end{infarray}

\subsection{The variable rule -- identity functions}
In the usual presentation of type theory, the variable rule asserts that ``in
the context $x_1:A_1,...,x_n:A_n$ we have a term $x_i:A_i$ when $1\leq i\leq n$''.

In our current system, we don't need this generality. Instead, it suffices for
us to assert that there are identity morphisms. We get arbitrary projections
from weakening.

\begin{infarray}{c}
\inference{\jtype{\Gamma}{A}}{\jtermt{\ctxext{\Gamma}{A}}{\ctxwk{A}{A}}{\idfunc[A]}}\\
\inference{\jtermt{\Gamma}{A}{x}}{\jtermteq{\Gamma}{A}{\subst{x}{\idfunc[A]}}{x}}\\
\inference{\jtermt{\ctxext{\Gamma}{A}}{P}{f}}{\jtermteq{\ctxext{\Gamma}{A}}{P}{\subst{\idfunc[A]}{\ctxwk{A}{f}}}{f}}\\
\inference{\jtermt{\ctxext{\Gamma}{B}}{\ctxwk{B}{A}}{g}}{\jtermteq{\ctxext{\Gamma}{B}}{\ctxwk{B}{A}}{\subst{g}{\ctxwk{B}{\idfunc[A]}}}{g}}
\end{infarray}

Using these rules we can derive that there is a judgmental equality $\jtypeeq{\ctxext{\Gamma}{A}}{\subst{x}{{\idfunc[A]}{B}}}
{\subst{x}{{x}{B}}}$.

%\begin{infarray}{c}
%\inference{\jtype{\ctxext{{\Gamma}{A}}{P}}{Q}\qquad\jtermt{\Gamma}{A}{x}\qquad\jtermt{\ctxext{A
%\end{infarray}{c}
